DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-04-20 paper/related.tex
related work revision

The XNOR operation and bit counting have been known to be efficient in
hardware implementations. In~\cite{rastegari2016xnor}, it was shown
that the binarized convolution could substitute the expensive
convolutional feedforward operations in a regular Convolutional Neural
Network (CNN), %% by using only about 1.5\% of the memory space, while
providing 20 to 60 times faster feedforward. Binary weights were also
able to provide 7 times faster feedforward than a floating-point
network for the hand written digit recognition task as well as 23
times faster matrix multiplication tasks on a
GPU~\cite{hubara2016binarized}.
Moreover, FPGA implementations showed that the XNOR operation is 200
times cheaper than floating-point multiplications with 
single precision~\cite{beauchamp2006embedded,govindu2004analysis}.
XNOR-POP is another hardware implementation that reduced
the energy consumption of a CNN by 98.7\%~\cite{jiang2017xnor}.

These research efforts are expected to make complex CNNs more
accessible for a wider range of real-time embedded systems. We plan to
investigate the feasibility of these approaches in the context of
DeepPicar so that we can use even more resource constrained
micro-controller class computing platforms.

>>>>

The XNOR operation and bit counting have been known to be efficient in
hardware implementations. In~\cite{rastegari2016xnor}, it was shown
that the binarized convolution could substitute the expensive
convolutional feedforward operations in a regular CNN, by using only
about 1.5\% of the memory space, while 
providing 20 to 60 times faster feedforward. Binary weights were also
able to provide 7 times faster feedforward than a floating-point
network for the hand written digit recognition task as well as 23
times faster matrix multiplication tasks on a
GPU~\cite{hubara2016binarized}.
Moreover, FPGA implementations showed that the XNOR operation is 200
times cheaper than floating-point multiplications with 
single precision~\cite{beauchamp2006embedded,govindu2004analysis}.
XNOR-POP is another hardware implementation that reduced
the energy consumption of a CNN by 98.7\%~\cite{jiang2017xnor}.

These research efforts are expected to make complex CNNs accessible
for a wider range of real-time embedded systems. We plan to 
investigate the feasibility of these approaches in the context of
DeepPicar so that we can use even more resource constrained
micro-controller class computing platforms in place of the current
Raspberry Pi 3.
